Luminance constancy under fixed geometry

### 2018-04-18 Draft4/draft4.tex
added RMSE values for condition 1
small edits

%% Figure 10: Results for Condition 1
\begin{figure}
\centering
        \begin{subfigure}[b]{0.3 \textwidth}
        \caption{RF response condition 1}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure10/Figure10_a.pdf}
        \label{fig:case1RFResponse}
    \end{subfigure}    
            \begin{subfigure}[b]{0.3 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure10/Figure10_b.pdf}
        \label{fig:case1Results}
    \end{subfigure}    
    \caption{{\bf RF response and luminance estimates for condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1. We show the response for the images in the training set. Each response cloud represents the response of images corresponding to one luminance level. The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure. (b) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA. The estimates fall along the diagonal unit slope (blue dotted) line for both linear regression and AMA. The standard deviations are too small to be visible. The relative error of estimation is XX (AMA) and YY(Linear regression).}
\label{fig:Condition1}
\end{figure}

Next, we discuss Condition 2, where we varied the spectral power distribution function of the light sources in addition to the target object LRV and relative spectrum. 
This is a more realistic condition, where the spectra of light sources change while the objects remain fixed, as in a naturalistic scene. 
Similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
First we trained and evaluated AMA on the cone responses to the image patches.
Figure~\ref{fig:isomerizationFails} shows the responses of the first two receptive fields to all the image patches in the training set.
For the spectral variations of condition 2, the AMA receptive fields learnt on the cone response to the images does a very poor job in predicting the target LRV.
This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
The decoding performance using these receptive fields for the test set is shown in Figure~\ref{fig:IsomerizationResults}.

>>>>

%% Figure 10: Results for Condition 1
\begin{figure}
\centering
        \begin{subfigure}[b]{0.3 \textwidth}
        \caption{RF response condition 1}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure10/Figure10_a.pdf}
        \label{fig:case1RFResponse}
    \end{subfigure}    
            \begin{subfigure}[b]{0.3 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure10/Figure10_b.pdf}
        \label{fig:case1Results}
    \end{subfigure}    
    \caption{{\bf RF response and luminance estimates for condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1. We show the response for the images in the training set. Each response cloud represents the response of images corresponding to one luminance level. The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure. (b) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA. The estimates fall along the diagonal unit slope (blue dotted) line for both linear regression and AMA. The standard deviations are too small to be visible. The relative error of estimation is 1.1\% (AMA) and 0.8\% (Linear regression).}
\label{fig:Condition1}
\end{figure}

Next we discuss Condition 2, where we varied the spectral power distribution function of the light sources in addition to the target object LRV and relative spectrum. 
This is a more realistic condition, where the spectra of light sources change while the objects remain fixed, as in a naturalistic scene. 
Similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
First we trained and evaluated AMA on the cone responses to the image patches.
Figure~\ref{fig:isomerizationFails} shows the responses of the first two receptive fields to all the image patches in the training set.
For the spectral variations of condition 2, the AMA receptive fields learnt on the cone response to the images does a very poor job in predicting the target LRV.
This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
The decoding performance using these receptive fields for the test set is shown in Figure~\ref{fig:IsomerizationResults}.
